---
title: "Traditional Chinese Medicines(TCM)"
---

### **_The Traditional/Herbal Chinese Medicines(TCM) have been applied in medical field in oriental countries for thousands of years and still plays important roll in current health care in those regions._**
#### **_中医在东方应用了数千年，对当地人的健康起了重要影响_**

### **_Although the theories looks different from modern medicine, there are thousands of herbs used &  prescriptions developed for treatment, and quite amount of them are considered 'effective'._**
#### **_尽管中医理论异于现代医学，其中数千草药、数万药方的治疗功效还是明显的_**

### **_By collecting & cleaning thousands of herbs & prescriptions record, I cleaned them (and will keep collecting them) in a modern data structure and make them ready for modern data analysis._**
#### **_在收集了大量药方后，我清理了数据，希望能用现代方法进行分析_**

```{r settings,echo=FALSE,results='hide',fig.keep='all', message=FALSE,warning=FALSE}
Sys.setlocale("LC_ALL","Chinese") #<--set for showing Chinese 
library(googlesheets4)
library(dplyr) #<-- for "select" function
library("wordcloud")
```

```{r gshets,echo=FALSE, message=FALSE,warning=FALSE}

gs4_deauth() #<--use only for googlesheets shared as 'anyone with the link'

rw_tcm <- read_sheet("https://docs.google.com/spreadsheets/d/1pRLlpF0hInmJ0XkA-qBrx2Koz8wHoGZTbbLz6t2x2Uc/edit?usp=sharing", sheet = "Sheet1")

```

---

### **_There are `r length(unique(rw_tcm$Corrected_ChName))` traditional Chinese medicine prescriptions collected._**

#### **_这里收集了 `r length(unique(rw_tcm$Corrected_ChName))`中药处方。_**

### **_The word cloud of the Cures that precriptions cure are as follow:_**

#### **_药方主治高频词图如下：_**

```{r dataClean,echo=FALSE, message=FALSE,warning=FALSE}

tcm_cl <- rw_tcm

# ---------- noun part ----------

cols_n <- max(stringr::str_count(na.omit(tcm_cl$CleanedCuresString),";")) + 1

colm_n <- paste("col_n",1:cols_n)

tcm_cl <-
  tidyr::separate(
    data = tcm_cl,
    col = CleanedCuresString,
    sep = ";",
    into = colm_n,
    remove = FALSE
  )

Cure_only <- select(tcm_cl,starts_with("col_n"))
Cures <- data.frame(Cure=na.omit(unlist(Cure_only))) #<--attach columns of values into one column
Cures$Cure <- factor(Cures$Cure,levels=as.character(names(sort(table(Cures$Cure),decreasing=T)))) 

Cure_freq <- as.data.frame(table(Cures$Cure))
Cure_freq2 <- Cure_freq[Cure_freq$Freq<50000,]

wordcloud(words=Cure_freq2$Var1,freq=Cure_freq$Freq,min.freq=1,
          max.words=100, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8,'Dark2'))
```
